Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-09 paper.tex
Rough in related work and conclusions.

% Nell focused on Literacy
% olpc context here?
\cite{chang:tinkrbook}
%context: english literacy, far from teachers & schools
\subsection{The Sugar Learning Environment}
% Sugar
%% customization
%% path through the educational material?
\subsection{Narrative computing}
% Reidl
\subsection{Storytelling}
% TinkRBooks

\section{Conclusions}

>>>>

The TinkRBook system~\cite{chang:tinkrbook} shares a similar focus on
personalization and literacy.  Project Nell attempts to scale these
ideas with a modular extensible narrative system and a broader range
of pedagogic material.

The Sugar Learning environment~\cite{XXX} is an earlier effort at
child education.  We've learned directly from this effort.  Nell
focuses on children even further from educational infrastructure.
The narrative at Nell's code attempts to provide students additional
pedagogical guidance, and the direct interaction model avoids keyboard
problems which have plagued Sugar's initial deployments.  Nell also
attempts to provide a greater sense of ownership through pervasive
customization.

Automatic narrative generation has seen attention in
gaming, simulation, and training contexts~\cite{riedlXXX}.  Nell's
use of these ideas in a pedagogical context is unique.

\section{Conclusions}
We have described the design of a novel narrative direct-interface
system for teaching literacy, which is personalized for and grows with
its child owner.  Personalized direct interface engages the child, and
narrative guides them through Nell's pedagogic material.  The low-cost
solar-powered hardware allows Nell to reach further into the
least-developed areas of the world, to help those far from traditional
educational infrastructure.

We are in the process of implementing the Nell system, and expect to
do initial deployments in Africa later this year.
